---
title: "BI612 H2"
author: "Natasha Hannan"
output: html_document
---

#Scenario 1
#a)State the null and alternative hypothesis
null hypothesis: there is no difference between shrimp catch from ships in 2009 and 2010
alternative hypothesis: there is a difference between shrimp catch from ships in 2009 and 2010

#b)Create a histogram
```{r}
firstcatch=c(91900,95200,61900,73600,114300,117000,129500,74200,112700,152100,90700,89400,127500,142200)
secondcatch=c(82900,86700,46900,41300,91600,100400,128400,55900,101700,139100,79300,76100,114100,139800)
hist(firstcatch-secondcatch)
```


#c)Explain what type of test should be used to test the hypothesis
In order to test the hypothesis, a paired t-test should be used

#d)Run the appropriate test, and display the summary output
```{r}
t.test(firstcatch, secondcatch, paired=TRUE)
```
#e)Explicitely state the critical and observed value of the test statistic
```{r}
qt(0.975,13)
qt(0.025,13)
observed=6.3808
```

#f)Indicate what conclusion you would draw from the hypothesis test
The p-value is small than 0.05, therefore we reject the null hypothesis. This means that there is a difference between shrimp catch from ships in 2009 and 2010 



#Scenario 2
#a)State the null and alternative hypothesis
null hypothesis: the phosphorus levels in the lake are within the guidelines
alternative hypothesis: the phosporus levels in the lake are higther than the guidelines

#b)Create a histogram
```{r}
phosphorous=c(18.4,12.9,15.3,18.3,15.6,23.3,16.5,12.3,24.6,16.2)
hist(phosphorous)
```

#c)Explain what type of test should be used to test the hypothesis
In order to test the hypothesis, a one-sample t-test should be used

#d)Run the appropriate test, and display the summary output
```{r}
t.test(phosphorous, mu=15)
```
#e)Explicitely state the critical and observed value of the test statistic
```{r}
qt(0.95,9)
observed=1.8462
```

#f)Indicate what conclusion you would draw from the hypothesis test

```{r}
p.value=0.09794/2
p.value
```
The p-value is small than 0.05, therefore we reject the null hypothesis. This means that the phosphorus levels in the lake are higher than the guidelines. 




#Scenario 3
#a)State the null and alternative hypothesis
null hypothesis: there is no difference in salmon growth rate when fed a vegetarian or carnivorous diet.
alternative hypothesis: there is a difference in salmon growth rate when fed a vegetarian or carnivorous diet.

#b)Create a histogram
```{r}
carnivorous=c(2.3,1.8,1.9,1.8,2.1,2.3,2.0,2.2,2.2,1.5,1.8,2.1,2.3,2.2,2.3)
vegetarian=c(1.6,1.1,0.7,1.0,1.0,0.9,1.2,0.8,0.9,0.6,0.7,0.6,0.8,0.8,1.1)
hist(carnivorous)
hist(vegetarian)
```


#c)Explain what type of test should be used to test the hypothesis
In order to test the hypothesis, an independent two-sample t-test should be used

#d)Run the appropriate test, and display the summary output
```{r}
t.test(carnivorous,vegetarian)
```
#e)Explicitely state the critical and observed value of the test statistic
```{r}
qt(0.975,27.862)
qt(0.025,27.862)
observed=12.237
```

#f)Indicate what conclusion you would draw from the hypothesis test
The p-value is small than 0.05, therefore we reject the null hypothesis. This means that there is a difference in salmon growth rate when fed a vegetarian or carnivorous diet. 


#Scenario 4
#a)State the null and alternative hypothesis
null hypothesis: there is no interaction between symptoms and the trophic level of the individual
alternative hypothesis: there is an interaction between symptoms and the trophic level of the individual

#b)Create a histogram
```{r}
first.trophic=c(133,100,17)
top.predator=c(4,61,35)
my.data=data.frame(first.trophic, top.predator)
```

#c)Explain what type of test should be used to test the hypothesis
In order to test the hypothesis, a Chi-squared test should be used

#d)Run the appropriate test, and display the summary output
```{r}
chisq.test(my.data)
```
#e)Explicitely state the critical and observed value of the test statistic
```{r}
qt(0.95,2)
observed=89.253
```
#f)Indicate what conclusion you would draw from the hypothesis test
The p-value is small than 0.05, therefore we reject the null hypothesis. This means that there is an interaction between symptoms and trophic levels.